
\begin{profile}
\footnotesize
\dirtree{%
.1  . 
.1 \textbf{71.67\%} dvmPlatformInvoke\newline \phantom{\textbf{71.67\%}} ---0x535d7cdc\newline \phantom{\textbf{71.67\%}} dvmPlatformInvoke. 
.2 \textbf{68.36\%} Java\_fi\_helsinki\_cs\_tituomin\_nativebenchmark\_benchmark\_C2JBenchmark00146\_runInternal. 
.3 \textbf{66.09\%} CallVoidMethod(\_JNIEnv*, \_jobject*, \_jmethodID*, ...). 
.4 \textbf{15.56\%} dvmCallMethodV(Thread*, Method const*, Object*, bool, JValue*, std::\_\_va\_list). 
.5 \textbf{3.68\%} dvmInterpret(Thread*, Method const*, JValue*). 
.6 \textbf{0.39\%} common\_selectTrace. 
.7 \textbf{0.10\%} dvmJitCheckTraceRequest. 
.8 \textbf{0.07\%} dvmJitFindEntry\newline \phantom{\textbf{0.07\%}} dvmJitHash(unsignedshortconst*). 
.6 \textbf{0.20\%} common\_updateProfile\newline \phantom{\textbf{0.20\%}} dvmJitGetTraceAddrThread. 
.7 \textbf{0.03\%} getCodeAddrCommon(unsigned short const*, bool)\newline \phantom{\textbf{0.03\%}} dvmJitHash(unsignedshortconst*). 
.5 \textbf{2.50\%} callPrep(Thread*, Method const*, Object*, bool). 
.5 \textbf{0.67\%} dvmPopFrame(Thread*). 
.4 \textbf{13.42\%} dvmDecodeIndirectRef(Thread*, \_jobject*) \ding{202}. 
.5 \textbf{4.24\%} ScopedPthreadMutexLock::ScopedPthreadMutexLock(pthread\_mutex\_t*). 
.6 \textbf{3.35\%} pthread\_mutex\_lock. 
.7 \textbf{2.20\%} pthread\_mutex\_lock\_impl. 
.5 \textbf{3.29\%} ScopedPthreadMutexLock::~ScopedPthreadMutexLock(). 
.6 \textbf{2.49\%} pthread\_mutex\_unlock. 
.7 \textbf{1.39\%} pthread\_mutex\_unlock\_impl. 
.5 \textbf{1.37\%} IndirectRefTable::get(void*) const. 
.4 \textbf{3.35\%} dvmGetVirtualizedMethod(ClassObject const*, Method const*)() \ding{203}. 
.5 \textbf{1.00\%} dvmIsDirectMethod(Method const*). 
.4 \textbf{3.07\%} ScopedJniThreadState::ScopedJniThreadState(\_JNIEnv*) \ding{204}. 
.5 \textbf{0.58\%} dvmChangeStatus(Thread*, ThreadStatus). 
.6 \textbf{0.31\%} android\_atomic\_acquire\_store. 
.7 \textbf{0.03\%} android\_memory\_barrier. 
.4 \textbf{2.45\%} ScopedJniThreadState::~ScopedJniThreadState()  \ding{204}. 
.5 \textbf{1.34\%} dvmChangeStatus(Thread*, ThreadStatus). 
.6 \textbf{0.39\%} android\_atomic\_release\_store. 
.7 \textbf{0.07\%} android\_memory\_barrier. 
.3 \textbf{0.03\%} PushLocalFrame(\_JNIEnv*, int). 
}
\end{profile}

