
\begin{profile}
\centering
\caption{Metodikutsu C$\rightarrow$Java 20 viiteparametrilla}
\label{profile:C2JBenchmark00206}
\begin{topbot}
\begin{minipage}{1.0\textwidth}
\scriptsize
\dirtree{%
.1 \textbf{71.09\%} Java\_fi\_helsinki\_cs\_tituomin\_nativebenchmark\_benchmark\_C2JBenchmark00206\_runInternal. 
.2 \textbf{70.19\%} CallVoidMethod(\_JNIEnv*, \_jobject*, \_jmethodID*, ...). 
.3 \textbf{56.30\%} dvmCallMethodV(Thread*, Method const*, Object*, bool, JValue*, std::\_\_va\_list). 
.4 \textbf{46.21\%} dvmDecodeIndirectRef(Thread*, \_jobject*)  \DTcomment{\ding{202}}. 
.5 \textbf{13.64\%} ScopedPthreadMutexLock::ScopedPthreadMutexLock(pthread\_mutex\_t*)  \DTcomment{\ding{203}}. 
.6 \textbf{11.09\%} pthread\_mutex\_lock. 
.7 \textbf{4.53\%} pthread\_mutex\_lock\_impl. 
.5 \textbf{12.26\%} ScopedPthreadMutexLock::~ScopedPthreadMutexLock()  \DTcomment{\ding{204}}. 
.6 \textbf{10.13\%} pthread\_mutex\_unlock. 
.7 \textbf{3.67\%} pthread\_mutex\_unlock\_impl. 
.5 \textbf{4.07\%} IndirectRefTable::get(void*) const  \DTcomment{\ding{205}}. 
.4 \textbf{1.12\%} dvmInterpret(Thread*, Method const*, JValue*). 
.5 \textbf{0.19\%} common\_selectTrace. 
.6 \textbf{0.13\%} dvmJitCheckTraceRequest. 
.5 \textbf{0.13\%} common\_updateProfile\newline \phantom{\textbf{0.13\%}} dvmJitGetTraceAddrThread. 
.6 \textbf{0.07\%} getCodeAddrCommon(unsigned short const*, bool). 
.4 \textbf{0.91\%} callPrep(Thread*, Method const*, Object*, bool). 
.4 \textbf{0.14\%} dvmPopFrame(Thread*). 
.3 \textbf{2.26\%} dvmDecodeIndirectRef(Thread*, \_jobject*). 
.4 \textbf{0.75\%} ScopedPthreadMutexLock::ScopedPthreadMutexLock(pthread\_mutex\_t*). 
.5 \textbf{0.54\%} pthread\_mutex\_lock. 
.6 \textbf{0.20\%} pthread\_mutex\_lock\_impl. 
.4 \textbf{0.40\%} ScopedPthreadMutexLock::~ScopedPthreadMutexLock(). 
.5 \textbf{0.34\%} pthread\_mutex\_unlock. 
.6 \textbf{0.13\%} pthread\_mutex\_unlock\_impl. 
.4 \textbf{0.31\%} IndirectRefTable::get(void*) const. 
.3 \textbf{0.82\%} dvmGetVirtualizedMethod(ClassObject const*, Method const*). 
.4 \textbf{0.17\%} dvmIsDirectMethod(Method const*). 
.3 \textbf{0.39\%} ScopedJniThreadState::ScopedJniThreadState(\_JNIEnv*). 
.4 \textbf{0.23\%} dvmChangeStatus(Thread*, ThreadStatus). 
.5 \textbf{0.03\%} android\_atomic\_acquire\_store. 
.3 \textbf{0.37\%} ScopedJniThreadState::~ScopedJniThreadState(). 
.4 \textbf{0.20\%} dvmChangeStatus(Thread*, ThreadStatus). 
.5 \textbf{0.10\%} android\_atomic\_release\_store. 
}
\end{minipage}
\end{topbot}
\end{profile}

