
\begin{profile}
\footnotesize
\dirtree{%
.1  . 
.1 \textbf{ 0.00\%} nativebenchmark  libdvm.so              [.] dvmPlatformInvoke\newline \phantom{\textbf{ 0.00\%}} ---dvmPlatformInvoke. 
.2 \textbf{68.25\%} Java\_fi\_helsinki\_cs\_tituomin\_nativebenchmark\_benchmark\_C2JBenchmark00001\_runInternal. 
.3 \textbf{64.83\%} CallStaticVoidMethod(\_JNIEnv*, \_jclass*, \_jmethodID*, ...). 
.4 \textbf{45.36\%} dvmCallMethodV(Thread*, Method const*, Object*, bool, JValue*, std::\_\_va\_list). 
.5 \textbf{10.95\%} dvmInterpret(Thread*, Method const*, JValue*). 
.6 \textbf{1.31\%} common\_selectTrace. 
.7 \textbf{0.22\%} dvmJitCheckTraceRequest. 
.8 \textbf{0.04\%} dvmJitFindEntry. 
.6 \textbf{0.43\%} common\_updateProfile. 
.7 \textbf{0.39\%} dvmJitGetTraceAddrThread. 
.8 \textbf{0.14\%} getCodeAddrCommon(unsigned short const*, bool). 
.5 \textbf{8.35\%} callPrep(Thread*, Method const*, Object*, bool). 
.5 \textbf{0.77\%} dvmPopFrame(Thread*). 
.4 \textbf{4.60\%} ScopedJniThreadState::~ScopedJniThreadState(). 
.5 \textbf{1.71\%} dvmChangeStatus(Thread*, ThreadStatus). 
.6 \textbf{0.48\%} android\_atomic\_release\_store. 
.7 \textbf{0.10\%} android\_memory\_barrier. 
.4 \textbf{4.50\%} ScopedJniThreadState::ScopedJniThreadState(\_JNIEnv*). 
.5 \textbf{1.64\%} dvmChangeStatus(Thread*, ThreadStatus). 
.6 \textbf{0.90\%} android\_atomic\_acquire\_store. 
.7 \textbf{0.43\%} android\_memory\_barrier. 
.3 \textbf{0.10\%} PopLocalFrame(\_JNIEnv*, \_jobject*). 
.4 \textbf{0.04\%} ScopedJniThreadState::~ScopedJniThreadState(). 
.3 \textbf{0.07\%} PushLocalFrame(\_JNIEnv*, int). 
.4 \textbf{0.04\%} dvmGetCurrentJNIMethod()\newline \phantom{\textbf{0.04\%}} . 
}
\end{profile}

