
\begin{profile}
\centering
\caption{Unicode-merkkijonon kopiointi C$\rightarrow$Java}
\label{profile:C2JCopyUnicode-512}
\begin{topbot}
\begin{minipage}{1.0\textwidth}
\scriptsize
\dirtree{%
.1 . 
.1 \textbf{70.31\%} dvmPlatformInvoke. %\newline \phantom{\textbf{ 0.00\%}} ---dvmPlatformInvoke. 
.2 \textbf{66.92\%} Java\_fi\_helsinki\_cs\_tituomin\_nativebenchmark\_benchmark\_C2JCopyUnicode\_runInternal. 
.3 \textbf{40.10\%} GetStringRegion(\_JNIEnv*, \_jstring*, int, int, unsigned short*). 
.4 \textbf{20.26\%} dvmDecodeIndirectRef(Thread*, \_jobject*). 
.5 \textbf{5.93\%} ScopedPthreadMutexLock::ScopedPthreadMutexLock(pthread\_mutex\_t*). 
.6 \textbf{5.28\%} pthread\_mutex\_lock. 
.7 \textbf{1.91\%} pthread\_mutex\_lock\_impl. 
.5 \textbf{4.07\%} ScopedPthreadMutexLock::~ScopedPthreadMutexLock(). 
.6 \textbf{3.64\%} pthread\_mutex\_unlock. 
.7 \textbf{1.72\%} pthread\_mutex\_unlock\_impl. 
.5 \textbf{2.71\%} IndirectRefTable::get(void*) const. 
.4 \textbf{4.20\%} ScopedJniThreadState::ScopedJniThreadState(\_JNIEnv*). 
.5 \textbf{1.34\%} dvmChangeStatus(Thread*, ThreadStatus). 
.6 \textbf{0.83\%} android\_atomic\_acquire\_store. 
.7 \textbf{0.16\%} android\_memory\_barrier. 
.4 \textbf{3.22\%} ScopedJniThreadState::~ScopedJniThreadState(). 
.5 \textbf{1.89\%} dvmChangeStatus(Thread*, ThreadStatus). 
.6 \textbf{0.71\%} android\_atomic\_release\_store. 
.7 \textbf{0.16\%} android\_memory\_barrier. 
.4 \textbf{1.85\%} StringObject::chars() const. 
.4 \textbf{0.29\%} StringObject::length() const. 
.3 \textbf{0.03\%} PopLocalFrame(\_JNIEnv*, \_jobject*)\newline \phantom{\textbf{0.03\%}} . 
.1 \textbf{22.08\%} nativebenchmark - libc.so [.] memcpy. %\newline \phantom{\textbf{22.08\%}} ---0x535d7d1c\newline \phantom{\textbf{22.08\%}} dvmPlatformInvoke\newline \phantom{\textbf{22.08\%}} Java\_fi\_helsinki\_cs\_tituomin\_nativebenchmark\_benchmark\_C2JCopyUnicode\_runInternal\newline \phantom{\textbf{22.08\%}} . 
}
\end{minipage}
\end{topbot}
\end{profile}

