
\begin{profile}
\centering
\caption{NewDirectByteBuffer}
\label{profile:C2JNewDirectBuffer-512}
\begin{topbot}
\begin{minipage}{1.0\textwidth}
\scriptsize
\dirtree{%
%.1 \textbf{ 0.02\%} dvmCallMethodV(Thread*, Method const*, Object*, bool, JValue*, std::\_\_va\_list). 
.2 \textbf{74.31\%} dvmCallMethodV(Thread*, Method const*, Object*, bool, JValue*, std::\_\_va\_list). 
.3 \textbf{73.83\%} dvmInterpret(Thread*, Method const*, JValue*). 
.4 \textbf{72.21\%} dalvik\_mterp\newline \phantom{\textbf{72.21\%}} Dalvik\_java\_lang\_Runtime\_gc(unsignedintconst*,JValue*)\newline \phantom{\textbf{72.21\%}} dvmCollectGarbage(). 
.5 \textbf{72.19\%} dvmCollectGarbageInternal(GcSpec const*). 
.6 \textbf{43.71\%} dvmHeapScanMarkedObjects(). 
.6 \textbf{19.92\%} dvmHeapSweepUnmarkedObjects(bool, bool, unsigned int*, unsigned int*). 
.6 \textbf{3.74\%} dvmHeapReScanMarkedObjects(). 
.6 \textbf{2.67\%} dvmHeapMarkRootSet()\newline \phantom{\textbf{2.67\%}} dvmVisitRoots(void(*)(void*,unsignedint,RootType,void*),void*). 
.6 \textbf{1.73\%} dvmHeapReMarkRootSet()\newline \phantom{\textbf{1.73\%}} dvmVisitRoots(void(*)(void*,unsignedint,RootType,void*),void*). 
.6 \textbf{0.09\%} dvmHeapFinishMarkStep(). 
.6 \textbf{0.02\%} dvmGetRelativeTimeMsec()\newline \phantom{\textbf{0.02\%}} dvmGetRelativeTimeUsec(). 
.6 \textbf{0.02\%} dvmHeapSweepSystemWeaks()\newline \phantom{\textbf{0.02\%}} dvmGcDetachDeadInternedStrings(int(*)(void*)). 
.4 \textbf{0.12\%} dalvik\_inst. 
.5 \textbf{0.10\%} dvmAllocObject\newline \phantom{\textbf{0.10\%}} dvmMalloc(unsignedint,int). 
.6 \textbf{0.04\%} dvmUnlockHeap()\newline \phantom{\textbf{0.04\%}} dvmUnlockMutex(pthread\_mutex\_t*)\newline \phantom{\textbf{0.04\%}} pthread\_mutex\_unlock. 
.7 \textbf{0.02\%} pthread\_mutex\_unlock\_impl. 
.6 \textbf{0.04\%} tryMalloc(unsigned int). 
.7 \textbf{0.02\%} dvmHeapSourceAlloc(unsigned int)\newline \phantom{\textbf{0.02\%}} countAllocation(Heap*,voidconst*). 
.6 \textbf{0.02\%} dvmLockHeap()\newline \phantom{\textbf{0.02\%}} dvmTryLockMutex(pthread\_mutex\_t*). 
.4 \textbf{0.04\%} common\_updateProfile. 
.5 \textbf{0.02\%} dvmJitGetTraceAddrThread\newline \phantom{\textbf{0.02\%}} getCodeAddrCommon(unsignedshortconst*,bool). 
.4 \textbf{0.03\%} common\_selectTrace. 
.3 \textbf{0.20\%} callPrep(Thread*, Method const*, Object*, bool). 
}
\end{minipage}
\end{topbot}
\end{profile}

