
\begin{profile}
\centering
\caption{Unicode-merkkijonon osoitinoperaatio}
\label{profile:C2JReadUnicode-512}
\begin{topbot}
\begin{minipage}{1.0\textwidth}
\scriptsize
\dirtree{%
.1 \textbf{69.25\%} dvmPlatformInvoke. %\newline \phantom{\textbf{69.25\%}} ---0x536d7d1c\newline \phantom{\textbf{69.25\%}} dvmPlatformInvoke. 
.2 \textbf{66.81\%} Java\_fi\_helsinki\_cs\_tituomin\_nativebenchmark\_benchmark\_C2JReadUnicode\_runInternal. 
.3 \textbf{34.09\%} GetStringChars(\_JNIEnv*, \_jstring*, unsigned char*). 
.4 \textbf{12.20\%} dvmDecodeIndirectRef(Thread*, \_jobject*). 
.5 \textbf{3.39\%} ScopedPthreadMutexLock::~ScopedPthreadMutexLock(). 
.6 \textbf{3.16\%} pthread\_mutex\_unlock. 
.7 \textbf{1.97\%} pthread\_mutex\_unlock\_impl. 
.5 \textbf{2.80\%} ScopedPthreadMutexLock::ScopedPthreadMutexLock(pthread\_mutex\_t*). 
.6 \textbf{2.31\%} pthread\_mutex\_lock. 
.7 \textbf{1.09\%} pthread\_mutex\_lock\_impl. 
.5 \textbf{0.96\%} IndirectRefTable::get(void*) const. 
.4 \textbf{8.44\%} pinPrimitiveArray(ArrayObject*). 
.5 \textbf{2.54\%} ScopedPthreadMutexLock::~ScopedPthreadMutexLock(). 
.6 \textbf{2.27\%} pthread\_mutex\_unlock. 
.7 \textbf{1.25\%} pthread\_mutex\_unlock\_impl. 
.5 \textbf{2.12\%} ScopedPthreadMutexLock::ScopedPthreadMutexLock(pthread\_mutex\_t*). 
.6 \textbf{1.75\%} pthread\_mutex\_lock. 
.7 \textbf{0.98\%} pthread\_mutex\_lock\_impl. 
.4 \textbf{4.73\%} ScopedJniThreadState::ScopedJniThreadState(\_JNIEnv*). 
.5 \textbf{2.77\%} dvmChangeStatus(Thread*, ThreadStatus). 
.6 \textbf{1.90\%} android\_atomic\_acquire\_store. 
.7 \textbf{0.03\%} android\_memory\_barrier. 
.4 \textbf{2.23\%} ScopedJniThreadState::~ScopedJniThreadState(). 
.5 \textbf{1.46\%} dvmChangeStatus(Thread*, ThreadStatus). 
.6 \textbf{0.49\%} android\_atomic\_release\_store. 
.7 \textbf{0.10\%} android\_memory\_barrier. 
.4 \textbf{0.42\%} StringObject::chars() const. 
.4 \textbf{0.28\%} StringObject::array() const. 
.3 \textbf{28.88\%} ReleaseStringChars(\_JNIEnv*, \_jstring*, unsigned short const*). 
.3 \ldots. 
}
\end{minipage}
\end{topbot}
\end{profile}
\newpage
\addtocounter{profile}{-1}
\begin{profile}
\caption{Unicode-merkkijonon osoitinoperaatio [jatkoa]}
\begin{topbot}
\begin{minipage}{1.0\textwidth}
\scriptsize
\dirtree{%
.1 . 
.2 \textbf{28.88\%} ReleaseStringChars(\_JNIEnv*, \_jstring*, unsigned short const*). 
.3 \textbf{8.56\%} dvmDecodeIndirectRef(Thread*, \_jobject*). 
.4 \textbf{2.53\%} ScopedPthreadMutexLock::ScopedPthreadMutexLock(pthread\_mutex\_t*). 
.5 \textbf{1.92\%} pthread\_mutex\_lock. 
.6 \textbf{0.88\%} pthread\_mutex\_lock\_impl. 
.4 \textbf{1.93\%} ScopedPthreadMutexLock::~ScopedPthreadMutexLock(). 
.5 \textbf{1.66\%} pthread\_mutex\_unlock. 
.6 \textbf{0.89\%} pthread\_mutex\_unlock\_impl. 
.4 \textbf{0.69\%} IndirectRefTable::get(void*) const. 
.3 \textbf{8.38\%} unpinPrimitiveArray(ArrayObject*). 
.4 \textbf{2.67\%} ScopedPthreadMutexLock::ScopedPthreadMutexLock(pthread\_mutex\_t*). 
.5 \textbf{1.91\%} pthread\_mutex\_lock. 
.6 \textbf{0.72\%} pthread\_mutex\_lock\_impl. 
.4 \textbf{2.35\%} ScopedPthreadMutexLock::~ScopedPthreadMutexLock(). 
.5 \textbf{2.01\%} pthread\_mutex\_unlock. 
.6 \textbf{1.26\%} pthread\_mutex\_unlock\_impl. 
.4 \textbf{0.69\%} dvmRemoveFromReferenceTable(ReferenceTable*, Object**, Object*). 
.3 \textbf{2.40\%} ScopedJniThreadState::~ScopedJniThreadState(). 
.4 \textbf{1.81\%} dvmChangeStatus(Thread*, ThreadStatus). 
.5 \textbf{0.71\%} android\_atomic\_release\_store. 
.6 \textbf{0.07\%} android\_memory\_barrier. 
.3 \textbf{1.63\%} ScopedJniThreadState::ScopedJniThreadState(\_JNIEnv*). 
.4 \textbf{0.95\%} dvmChangeStatus(Thread*, ThreadStatus). 
.5 \textbf{0.70\%} android\_atomic\_acquire\_store. 
.6 \textbf{0.06\%} android\_memory\_barrier. 
.3 \textbf{0.23\%} StringObject::array() const. 
.2 \textbf{0.09\%} PushLocalFrame(\_JNIEnv*, int). 
.3 \textbf{0.06\%} dvmGetCurrentJNIMethod(). 
.3 \textbf{0.03\%} ScopedJniThreadState::ScopedJniThreadState(\_JNIEnv*)\newline \phantom{\textbf{0.03\%}} dvmChangeStatus(Thread*,ThreadStatus). 
.2 \textbf{0.03\%} PopLocalFrame(\_JNIEnv*, \_jobject*). 
}
\end{minipage}
\end{topbot}
\end{profile}

